---
title: "p8105_hw1_xh2636"
author: "Xiaoyu Huang"
date: "2023-09-19"
output: html_document
---

For This HW1
------------------------------------------------------------
I download the a package containing the penguins dataset by copy the code: install.packages("moderndive") in the console directly.

Then I use the following code to load the early_january_weather dataset.

# Problem 1

```{r, echo=FALSE}
library(moderndive)
data("early_january_weather")
```

Variable - describe the dataset:
------------------------------------------------------------

*   Temp
*   Dewp
*   Humid
*   Wind speed
*   Wind dir
*   Hour
*   Pressure
*   Precip
*   Visible

Size of the dataset
------------------------------------------------------------
#The number of column of this dataset:
```{r, echo=FALSE}
weather_col<-ncol(early_january_weather)
print(weather_col)
```

#The number of row of this dataset:
```{r echo=FALSE}
weather_row<-nrow(early_january_weather)
print(weather_row)
```

# Mean temperature
```{r, echo=FALSE}
x <- mean(early_january_weather$temp)
mean(x)
```

# Scatterplot of Temp (y) vs Time hour (x)
```{r, include=FALSE}
library(tidyverse)
```

```{r, echo=FALSE}
scatter_plot <- ggplot(early_january_weather, 
                       aes(y = temp, x = time_hour, color = humid)) +
                         geom_point()
print(scatter_plot)
```

The pattern of this plot is swinging up and down like a wave. Also the humidity before Jan 07 is lower than the humidity after Jan 07.

```{r, echo=FALSE}
ggsave("scatter_plot.png")
```

# Problem 2

```{r, echo=FALSE}
example_df = tibble(
  vec_char = c("My","name","is","Gavin",
               "I","like","hiking","with","my","friends"),
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_factor = factor(c("excellent","fair","bad",
                        "excellent","fair","bad",
                        "excellent","fair","bad",
                        "excellent"))
)
example_df
```

# Random sample of size 10's mean:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
k <- example_df %>% pull(vec_char) %>% mean
z <- example_df %>% pull(vec_numeric) %>% mean
p <- example_df %>% pull(vec_logical) %>% mean
h <- example_df %>% pull(vec_factor) %>% mean
print(k)
print(z)
print(p)
print(h)
```

As we calculated the mean for these 4 variable, we found that the vec_numeric and vec_logic can have a mean, and other 2 variable does not. This is because the vec_logic in R, TRUE treat as 1 and FALSE treat as 0, so if the number is bigger than 0.5, which mean the data we collected have more TRUE than FALSE, vice versa. The other 2 variable is not numeric so they don't have a mean.

```{r, warning=FALSE, results='hide'}
print(as.numeric(example_df$vec_char))
print(as.numeric(example_df$vec_logical))
print(as.numeric(example_df$vec_factor))
```

From the result we can see that vec_char still can not have a numeric value, all the answer is NA, but for vec_logical we can have a numeric value and this is because R turn TRUE treat as 1 and FALSE treat as 0. For the vec_factor, it return integer codes corresponding to factor levels, which may not always be meaningful as numeric values.
